The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-20 ms.Rmd
trying another way of rendering the figures

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = FALSE}
# set up knitr options
opts_chunk$set(fig.path = 'figs/',
               message = FALSE,
               dev = c('pdf', 'png'),
               cache = TRUE)

@@

```{r plotzoonoverview, echo = FALSE, fig.height = 9, fig.cap = pzocap}

@@

```{r fengworkCaptions, eval = TRUE, echo = FALSE}
fengworkcap <- '
  Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence).
  White areas are masked due to being marine in the marine environment or due to the MESS mask [@Elith2010]
'
```

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE, fig.cap = fengworkcap}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))

@@

@@

```{r mewoChangeWorkflow, eval = FALSE}
Merow_Silander_Spatial <- ChangeWorkflow(
    merow_and_silander,
    process = Chain(..., PartitionDisc))
```

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = FALSE}
# set up knitr options
opts_chunk$set(fig.path = 'figs/',
               message = FALSE,
               dev = c('png'),
               cache = TRUE)

@@

```{r plotzoonoverview, echo = FALSE, fig.height = 9, dpi = 300, fig.cap = pzocap}

@@

```{r fengworkflow, eval = TRUE, results = 'hide', fig.show = 'hide', message = FALSE}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))

@@

![Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence). White areas are masked due to being marine in the marine environment or due to the MESS mask.\label{fig:fengmap](./figs/fengworkflow-1.png)

@@

```{r merowChangeWorkflow, eval = FALSE}
Merow_Silander_Spatial <- ChangeWorkflow(
    merow_and_silander,
    process = Chain(..., PartitionDisc))
```
